\textls[-0]{\thetitle}

### 2022-11-11 agda-files.tex

@@

This is the first QIIT-model we give. A QIIT-model can be roughly consider as an arbitrary mapping from the QIIT data (our syntax in this case), also respecting the quotient (judgmental equality in this case). Here, the syntactic translation model is mapping to (a subpart of) the original QIIT data (itself).

>>>>

We suggest reading these files in an editor with syntax highlighting for Agda
(e.g., \mbox{VS~Code} with the \textsf{language-agda}\footnote{\url{https://marketplace.visualstudio.com/items?itemName=j-mueller.agda}}
extension enabled).

@@

This is the first QIIT-model we give. A QIIT-model can be roughly consider as an arbitrary mapping from the QIIT data(our syntax in this case), also respecting the quotient(judgemental equality in this case). Here, the syntactic translation model is mapping to (a subpart of) the original QIIT data (itself).
